High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 conclusion.tex
Acknowledgements.
another comment non-addressed.

\ifreview
Comments to address in this section:
\begin{itemize}
	\color{red} 
	\item REVIEWER 2: How does Summit, the TITAN successor, compare to the
	conclusions? The end of the TITAN life-cycle basically invalidates the
	applicability of all conclusions if this generalisation is missing.
	\item REVIEWER 3: This statement in the "conclusions" section is quite
	exaggerated: "The experience captured in this paper will prove invaluable
	for designing WMS for computational campaigns and will provide a baseline
	to evaluate the relative merits of different approaches." WMS systems for
	LHC experiments have been developed and run in production for many years;
	while this paper adds interesting experience and data points, it's
	unlikely that this will be "invaluable" for new designs and a cornerstone
	for their evaluation.
\end{itemize}
\fi

@@

HEP was amongst the first, if not the first experimental community to realize
the importance of using WMS to manage their computational campaign(s). As
computing becomes increasingly critical for a range of experiments, the
experience foreshadows the importance of WMS for other experiments (such as
SKA, LSST etc.).  These experiments will have their own workload
characteristics, resources types and federation constraints, as well metrics
of performance. The experience captured in this paper will prove invaluable
for designing WMS for computational campaigns and will provide a baseline to
evaluate the relative merits of different approaches.

@@

>>>>

% \ifreview
% Comments to address in this section:
% \begin{itemize}
% 	\color{red} 
% 	% \item REVIEWER 2: How does Summit, the TITAN successor, compare to the
% 	% conclusions? The end of the TITAN life-cycle basically invalidates the
% 	% applicability of all conclusions if this generalisation is missing.
% 	% \item REVIEWER 3: This statement in the "conclusions" section is quite
% 	% exaggerated: "The experience captured in this paper will prove invaluable
% 	% for designing WMS for computational campaigns and will provide a baseline
% 	% to evaluate the relative merits of different approaches." WMS systems for
% 	% LHC experiments have been developed and run in production for many years;
% 	% while this paper adds interesting experience and data points, it's
% 	% unlikely that this will be "invaluable" for new designs and a cornerstone
% 	% for their evaluation. \jhanote{I think this comment can also be ignored.}
% \end{itemize}
% \fi

@@

HEP was amongst the first, if not the first experimental community to realize
the importance of using WMS to manage their computational campaign(s). As
computing becomes increasingly critical for a range of experiments, the
experience foreshadows the importance of WMS for other experiments (such as
SKA, LSST etc.).  These experiments will have their own workload
characteristics, resources types and federation constraints, as well metrics
of performance. The experience captured in this paper should be useful
for designing WMS for computational campaigns and will provide a baseline to
evaluate the relative merits of different approaches.

@@

{\bf \footnotesize This work is funded by DOE XXXXXX \par}

### 2017-09-10 nge.tex

\ifreview
Comments to address in this section:
\begin{itemize}
	\color{red} 
	\item REVIEWER 3: The first paragraphs of section V. are basically a
	rediscovery of the advantages of pilot jobs for WLCG task scheduling.
	Since all those pain points were well-known in the WLCG community before
	the project started, it should be explained why a pilot job approach was
	not taken in the first place.\mtnote{Added an opening paragraph recalling
	the explanation offered in \S\ref{sec:panda_titan}}.
	\item REVIEWER 3: Figure 6. refers to a "User Workstation" as the running
	place for the Pilot and Unit Managers, which is never mentioned in the
	text. (I got the impression that the NGE would run on a DTN node; if this
	is not the case and separate workstations are being used for the testing
	phase, this should be made clear.)\mtnote{Fixed.}
\end{itemize}
\fi

>>>>

% \ifreview
% Comments to address in this section:
% \begin{itemize}
% 	\color{red} 
% 	% \item REVIEWER 3: The first paragraphs of section V. are basically a
% 	% rediscovery of the advantages of pilot jobs for WLCG task scheduling.
% 	% Since all those pain points were well-known in the WLCG community before
% 	% the project started, it should be explained why a pilot job approach was
% 	% not taken in the first place.\mtnote{Added an opening paragraph recalling
% 	% the explanation offered in \S\ref{sec:panda_titan}}.
% 	% \item REVIEWER 3: Figure 6. refers to a "User Workstation" as the running
% 	% place for the Pilot and Unit Managers, which is never mentioned in the
% 	% text. (I got the impression that the NGE would run on a DTN node; if this
% 	% is not the case and separate workstations are being used for the testing
% 	% phase, this should be made clear.)\mtnote{Fixed.}
% \end{itemize}
% \fi

### 2017-09-10 overall.tex

    \item REVIEWER 2: Given an expected increase in resource need of 10-100,
    how is the capacity of 4\% WLCG significant? How does this relate to the
    manpower required to develop and maintain a custom solution per HPC site?
    How many TITAN resources are actually available to HEP, given the use by
    other domains? The magnitude of capacities presented as available is in
    major contrast to the requirements sketched in the introduction.

>>>>

    % \item REVIEWER 2: Given an expected increase in resource need of 10-100,
    % how is the capacity of 4\% WLCG significant? How does this relate to the
    % manpower required to develop and maintain a custom solution per HPC site?
    % How many TITAN resources are actually available to HEP, given the use by
    % other domains? The magnitude of capacities presented as available is in
    % major contrast to the requirements sketched in the introduction.
